Pillar 2 - Topic Modeling

### 2019-03-13 Pillar 2 - Topic Modeling.Rmd
re-arranges structure to compute things (e.g. perplexity) manually

)
```
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

## Fitting Model

From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics. Then we save them in the `Output`folder and in the ``Recommender System` folder.

#NEW
# LDA
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

```{r my_LDA, eval= TRUE}

@@

```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```

```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

@@

```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```
#Saving DELETE LATER
```{r saving tidy models, eval= TRUE}
save(topic_model_gb,
     file = "Output/topic_model_gb.RDATA")

save(topic_model_gb,
     file = "App/Recommender System/topic_model_gb.RDATA")
```
#Saving DELETE LATER
```{r saving models, eval= TRUE}
save(topic_model,
     file = "Output/topic_model.RDATA")

save(topic_model,
     file = "App/Recommender System/topic_model.RDATA")
```

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```
###Previous code DELETE LATER
```{r LDA fitxxxxxxx, cache = TRUE}
n_topics <- c(35, 35, 40)
levels   <- c("description", "overview", "manual")
list_nam <- character(0)

for(i in seq_along(n_topics)){

  dataset   <- get(paste("d", levels[i], "cast", sep = "_"))

  LDA_model <- LDA(
    x       = dataset,
    k       = n_topics[i],
    method  = "Gibbs",
    control = my_control
    )

  nam <- paste("LDA", levels[i], n_topics[i], sep = "_")

  assign(
    x     = nam,
    value = LDA_model
  )

  list_nam <- c(list_nam, nam)

save(list = list_nam,
     file = "Output/topic_model.RDATA")

save(list = list_nam,
     file = "App/Recommender System/topic_model.RDATA")
```

## Visualization
### Functions
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(results){

  tidy(results, matrix = "beta") %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

prepare_data_LDA_gamma <- function(results, level = Course){

  data_gamma <- tidy(results, matrix = "gamma") %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

@@

# Bet Distribution
LDA_description_120 %>% prepare_data_LDA_beta

# Gamma Distribution
LDA_description_120 %>% prepare_data_LDA_gamma(level = Cluster)
```

```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){

>>>>

)
```

###With Package built in Function
The function `my_FindTopicsNumber` builds a Topic Model and applies the measurements 
```{r function my_FindTopicsNumber }
my_FindTopicsNumber <- function(data_cast, n_topics){

@@

### Manually
The function `my_cast_tdm` casts our dataframes into a tdm.
```{r my_cast_tdm, eval = TRUE}
my_cast_tdm <- function(data) data %>%
  count(`Course ID`, word) %>%
  cast_dtm(`Course ID`, word, n)

@@

The function `my_LDA` fits an LDA model on the DTM using the previous controls.
```{r my_LDA, eval= TRUE}

@@

```
####10-fold Cross-validation
TO BE FINISHED
```{r manual evaluation, cache = TRUE, eval = TRUE}
set.seed(1234)

#number of topics for trials
n_topic = seq(from = 2, to = 80, by = 2)

#create folds
create_folds <- function(my_dtm){
  #find number of documents (D)
  D <- nrow(my_dtm)

  #Assign documents to a fold
  folding <- sample(rep(seq_len(10), ceiling(D))[seq_len(D)])
}

#
##Create folds
###Find number of documents
D_overview <- nrow(d_cast$overview)
D_manual <- nrow(d_cast$manual)

###Assigning random numbers (1:10) to each row of our DTM
folding_overview <- sample(rep(seq_len(10), ceiling(D_overview))[seq_len(D_overview)])
folding_manual   <- sample(rep(seq_len(10), ceiling(D_manual))[seq_len(D_manual)])

for(k in n_topics){
  for(chain in 1:10){
    ###Divide into training and testing sets
      #overview
    training_set_overview <- d_cast$overview[folding!=chain,]
    test_set_overview     <- d_cast$overview[folding==chain,]
      #manual
    training_set_manual   <- d_cast$manual[folding!=chain,]
    test_set_manual       <- d_cast$manual[folding==chain,]

  }
}

```
## Fitting Model
From the results we see that the ideal number of topics is somewhere between 35 and 40. We train our models on 35 topics. Then we save them in the `Output`folder and in the ``Recommender System` folder.

#NEW
# LDA
```{r LDA fit, cache = TRUE, eval = TRUE}
topic_model <- tibble(

@@

  mutate(
    TM_overview = n_topic %>% map( .f = my_LDA, corpus = d_cast$overview),
    TM_manual   = n_topic %>% map( .f = my_LDA, corpus = d_cast$manuals)
  )
```
##Model Evaluation
Perplexity is a measure of how well a probability model predicts a sample. Thus we need to do cross validation. 
```{r}

#Extracting LDA model n_topics = 2
test1 <- topic_model$TM_overview[1]

#Getting A single LDA Model:
test2 <- test1[[1]]

#getting perplexity
perplexity(test2, d_cast$overview, estimate_theta=FALSE)

Topic <- topics(test2)
Terms <- terms(test2,5)

lL <- list()
for(i in 1:length(topic_model$n_topic)){

  tmp <- topic_model$TM_overview[i]
  lL[[paste("n", 2*i)]] <- tmp[[1]]@loglikelihood

test1[[1]]@loglikelihood

log_like <- logLik(test1[[1]])

```
##Get Beta/Gamma functions
```{r getting gamma and beta, eval = TRUE}
get_beta <- function(results){

@@

##Apply beta and gamma
```{r applying get_gamma and get_beta, eval = TRUE}
topic_model_gb <- topic_model %>%
  transmute(
    n_topic    = n_topic,
    g_overview = TM_overview %>% map( .f = get_gamma),
    g_manual   = TM_manual   %>% map( .f = get_gamma),
    b_overview = TM_overview %>% map( .f = get_beta),
    b_manual   = TM_manual   %>% map( .f = get_beta)
      )
```

@@

#
##courses following_semester
course_following_semester <- sample(
  x       = course_all,
  size    = 60,
  replace = FALSE
  ) %>% sort
```
## Saving files for APP
```{r app files}
save(distribution, kw, course_all, course_following_semester,
     file = "App/Recommender System/data_topic_models.RDATA")
```

## Visualization
### Functions 
This part is adapted 
```{r LDA prepare, eval = F}
prepare_data_LDA_beta <- function(d_beta){

  data.frame(d_beta) %>%
    mutate(topic = paste("Topic", topic)) %>%
      group_by(topic) %>%
        top_n(10, beta) %>%
      ungroup %>%
      arrange(topic, desc(beta))

} #repetition??? of inspect topics?

prepare_data_LDA_gamma <- function(d_gamma, level = Course){

  data_gamma <- data.frame(d_gamma) %>%
    mutate(topic = paste("Topic", topic)) %>%
    rename(`Course ID` = document)

@@

# Bet Distribution
test <- list()

a <-  names(distribution)[1]
test[[a]] <- lapply(distribution[[a]],
                      prepare_data_LDA_beta)

# Gamma Distribution
b <- names(distribution)[2]
test[[b]] <- lapply(distribution[[b]],
                    prepare_data_LDA_gamma)

rm(a,b #,test
   )
```
This part is not adapted
```{r LDA visualize, eval = F}
visualize_LDA_beta <- function(data_prepared, id_plot = "test"){
